Speed and strength of epidemic intervention

### 2019-07-09 doc/speedstrength.tex
more

Renewal equation:
\begin{equation}
i(t) = S(t) \int K(s) i(t-s) ds
\end{equation}

Euler-Lotka:
\begin{equation}
1/\RR = \int g(s) \exp(-rs) ds
\end{equation}

@@

>>>>

Here, we use the renewal equation to model disease incidence $i(\tau)$:
\begin{equation}
i(\tau) = S(\tau) \int K(s) i(\tau-s) ds,
\end{equation}
where current incidence $i(\tau)$ is expressed as a product of the proportion of the population susceptible $S(\tau)$ and the current infectiousness of all previously infected individuals $\int K(s) i(\tau - s) ds$.
In the beginning of an epidemic, the proportion of population susceptible remains roughly constant ($S(\tau) \approx 1$) and this model simplifies to the Von Foerster equation [CITE Fraser et al.];
during this period, we expect the epidemic to grow exponentially.
Substituting $i(t) = i(0) \exp(rt)$ to (?) allows us to link speed and strength of an epidemic via the generation-interval distribution:
\begin{equation}
1/\RR = \int g(s) \exp(-rs) ds.
\end{equation}

@@

We assume that the effectiveness of intervention strategies $L(\tau)$ varies over the course of infection.
